### 2019-06-03 10_appendix.tex
update

The cost ratio is
\vspace{-0.1in}
\begin{equation}\label{eq:kmakespan-ratio}
\frac{C_{\rm k{\text-}arm}^t}{C_{\rm single}} \approx 
\frac{(c_{pd} + 0.52c_t)\frac{n}{k} + nf(k,r)c_t}{(c_{pd} + 0.52c_t)n}
= \frac{1}{k} + \frac{f(k,r)c_t}{c_{pd} + 0.52c_t}\;.
% \vspace{-0.1in}
\end{equation}

@@

In the unit square model, $a=b=1$. Substituting the values, the \textit{pdf} becomes
\begin{align}
p(l)&= 2\pi l - 8\pi l^2 + 2l^3, \ \ l\in[0,1]\\
p(l)&= 4l\sininv(\frac{1}{l}) - 4l\cosinv(\frac{1}{l}) + 8l\sqrt[]{(l^2-1)} -2l^3 -4l, \ \ l\in[1,\sqrt[]{2}]
\end{align}

Assuming two random sets of lines, representing transfers in a random split of objects between two arms, we need the expected value of the maximum of these pairwise lengths ie., $\mathtt{E}(max(l_1,l_2)), \ \ l_1,l_2\ i.i.d, \ \ l_1 \sim p, l_2 \sim p$.
This is estimated using the \textit{pdf} obtained. 
\begin{equation}
\mathtt{E}(max(l_1,l_2)) = \int_0^{\sqrt[]{2}} \int_0^{\sqrt[]{2}} max(l_1,l_2)p(l_1)p(l_2) dl_2 dl_1 \approx 0.663
\end{equation}
The result is calculated by taking into account the combination of different ranges of $p(l)$ and $max(l_1,l_2)$.
\commentadd{
\begin{wrapfigure}{r}{1.4in}
	\centering
	\vspace{-0.3in}
    \includegraphics[width=1.4in]{figures/monte_carlo}
	\caption{Empirical cost ratio versus the estimate}
  	\label{fig:bounds}
\end{wrapfigure}

@@

Using this result, the synchronized cost ratio is stated in Equation~\ref{eq:synchronized-ratio} as
$$
\frac{C_{\rm dual}^{\rm sync}}{C_{\rm single}} \approx 
\frac{(c_{pd} + 0.66c_t)\frac{n}{2} + 4n\pi rc_t}{(c_{pd} + 0.52c_t)n}
$$
As a way to validate our asymptotic estimate, randomized trials were run with different number randomly sampled object transfer coordinates on an unit square.
% Fig \ref{fig:bounds} verifies empirically that the ratio of $\frac{C_{dual}^{sync}}{C_{single}}$ when $c_{pd}=0,r=0$, asymptotically converges to the calculated expected value of $0.636$. 
When $c_{pd}=0$ and $r=0$, the ratio of $\frac{C_{dual}^{sync}}{C_{single}}$ evaluates to $0.636$. Fig \ref{fig:bounds} verifies empirically that the ratio converges to the expected value as the number of transfers increases.
This indicates the asymptotic speedup of a synchronized dual arm solution for a makespan or maximum of distances cost metric.
}

@@

% \vspace{-0.2in}
\begin{figure}
	\centering
	\includegraphics[width=2.3in]{figures/results/sp_smoothing}
	\includegraphics[width=2.3in]{figures/results/kuka_smoothing}
	\caption{Smoothed solution improvement as a percentage of the original synchronized solution duration, and the time taken to smooth solutions obtained from \algo in seconds.}
	\label{fig:smoothing}
%     \vspace{-.3in}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=5.3in]{figures/reachability}
	\includegraphics[width=5.3in]{figures/results/5_kuka_lazy_ms_success.png}
	\includegraphics[width=5.3in]{figures/results/5_kuka_lazy_ms_cost.png}
	\includegraphics[width=5.3in]{figures/results/5_kuka_lazy_ms_time.png}
	\caption{The reachability benchmark}
	\label{fig:reachability_benchmark}
%     \vspace{-.3in}
\end{figure}

>>>>

The cost ratio is
\vspace{-0.1in}
\begin{align*}\label{eq:kmakespan-ratio}
\frac{C_{\rm k{\text-}arm}^t}{C_{\rm single}} &\approx 
\frac{(c_{pd} + 0.52c_t)\frac{n}{k} + nf(k,r)c_t}{(c_{pd} + 0.52c_t)n}
\\&= \frac{1}{k} + \frac{f(k,r)c_t}{c_{pd} + 0.52c_t}\;.\numberthis
% \vspace{-0.1in}
\end{align*}

@@

In the unit square model, $a=b=1$. Substituting the values, the \textit{pdf} becomes
\begin{align*}
p(l)&= 2\pi l - 8\pi l^2 + 2l^3, \ \ l\in[0,1]\\
p(l)&= 4l\sininv(\frac{1}{l}) - 4l\cosinv(\frac{1}{l}) + 8l\sqrt[]{(l^2-1)} -2l^3 -4l,\\ &\ l\in[1,\sqrt[]{2}]
\end{align*}

Assuming two random sets of lines, representing transfers in a random split of objects between two arms, we need the expected value of the maximum of these pairwise lengths ie., $\mathtt{E}(max(l_1,l_2)), \ \ l_1,l_2\ i.i.d, \ \ l_1 \sim p, l_2 \sim p$.
This is estimated using the \textit{pdf} obtained. 
\begin{align*}
\mathtt{E}(max(l_1,l_2)) &= \int_0^{\sqrt[]{2}} \int_0^{\sqrt[]{2}} max(l_1,l_2)p(l_1)p(l_2) dl_2 dl_1\\&\approx 0.663
\end{align*}
The result is calculated by taking into account the combination of different ranges of $p(l)$ and $max(l_1,l_2)$.
\commentadd{
\begin{figure}[h]
	\centering
%	\vspace{-0.3in}
    \includegraphics[width=0.35\textwidth]{figures/monte_carlo}
	\caption{Empirical cost ratio versus the estimate}
  	\label{fig:mcbounds}
\end{figure}

@@

Using this result, the synchronized cost ratio is stated in Equation~\ref{eq:synchronized-ratio} as
$$
\frac{C_{\rm dual}^{\rm sync}}{C_{\rm single}} \approx 
\frac{(c_{pd} + 0.66c_t)\frac{n}{2} + 4n\pi rc_t}{(c_{pd} + 0.52c_t)n}
$$
As a way to validate our asymptotic estimate, randomized trials were run with different number randomly sampled object transfer coordinates on an unit square.
% Fig \ref{fig:bounds} verifies empirically that the ratio of $\frac{C_{dual}^{sync}}{C_{single}}$ when $c_{pd}=0,r=0$, asymptotically converges to the calculated expected value of $0.636$. 
When $c_{pd}=0$ and $r=0$, the ratio of $\frac{C_{dual}^{sync}}{C_{single}}$ evaluates to $0.636$. Fig \ref{fig:mcbounds} verifies empirically that the ratio converges to the expected value as the number of transfers increases.
This indicates the asymptotic speedup of a synchronized dual arm solution for a makespan or maximum of distances cost metric.
}

@@

% \vspace{-0.2in}
\begin{figure}[h]
	\centering	
	\includegraphics[width=0.48\textwidth]{figures/results/labels}
	\includegraphics[width=0.48\textwidth]{figures/results/sp_smoothing}
	\includegraphics[width=0.48\textwidth]{figures/results/kuka_smoothing}
	\caption{Smoothed solution improvement as a percentage of the original synchronized solution duration, and the time taken to smooth solutions obtained from \algo in seconds.}
	\label{fig:smoothing}
%     \vspace{-.3in}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.48\textwidth]{figures/reachability}
	\includegraphics[width=0.48\textwidth]{figures/results/labels}
	\includegraphics[width=0.48\textwidth]{figures/results/5_kuka_lazy_ms_success.png}
	\includegraphics[width=0.48\textwidth]{figures/results/5_kuka_lazy_ms_cost.png}
	\includegraphics[width=0.48\textwidth]{figures/results/5_kuka_lazy_ms_time.png}
	\caption{The reachability benchmark}
	\label{fig:reachability_benchmark}
%     \vspace{-.3in}
\end{figure}
